
---
title: "Rpolyhedra"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rpolyhedra}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
# Introduction
This package is a curation made based on the poly package found on http://www.netlib.org/polyhedra/ ([Original Help message](poly_original_help_message.html)), and the polyhedra database found on http://dmccooey.com/polyhedra, both of which provide polyhedra databases on its own format. As such, Rpolyhedra provides with the following:

1. A module to scrape the polyhedra for the different sources found with features for incremental correction of issues found and to be found in scraping process.
1. A database of the scraped polyhedra.
1. An R6 polyhedron representation with 'rgl' package visualizing capabilites. 

# Usage

For final users, the package provides a common interface for accesing public polyhedra databases, analize properties, compare and visualize them with RGL. 

For advanced users, the package provides a simplified set of R6 objects to scrape and compare polyhedra databases. 
```{r setup, include=FALSE}
library(rgl)
library(Rpolyhedra)
setupKnitr()
```


## Get available polyhedra
Once the original files had been processed, a simple call to ```getAvailablePolyhedra()``` retrieves a list of the available polyhedra with properties and status in the polyhedra database:

```{r availablePolyhedra}
#show only the first 10 polyhedra.
head(getAvailablePolyhedra(), n = 10)
```

## Retrieve a polyhedron
The access to a particular polyhedron can be done with a call to ```getPolyhedron(<<source>>, <<polyhedron.name>>)```, which returns a Polyhedron object. For example, to retrieve a cube from the netlib database, the call would be:

```{r getPolyhedron}
cube <- getPolyhedron(source = "netlib", polyhedron.name = "cube")
```

# A demo
To try package funcionality, a simple demo can be executed which shows the 5 regular polyhedra.

```{r demo, webgl=TRUE}
polyhedra.2.draw <- getAvailablePolyhedra(source = "netlib")
polyhedra.2.draw <- polyhedra.2.draw[polyhedra.2.draw$scraped.name %in%
        c("tetrahedron",
          "octahedron",
          "cube",
          "icosahedron",
          "dodecahedron"),]

n <- nrow(polyhedra.2.draw)
polyhedron.colors <- rainbow(n)
polyhedron.scale <- 5
open3d()
par3d(FOV = 1)
rgl.bg( sphere =FALSE, fogtype = "none", color=c("black"))
rgl.viewpoint(theta = 0,phi=0,zoom=0.8,fov=1)
for (i in seq_len(n)) {
  polyhedron.row <- polyhedra.2.draw[i,]
  polyhedron.name <- polyhedron.row$scraped.name
  polyhedron <- getPolyhedron(source = polyhedron.row$source, polyhedron.name)
  current.angle <- i/n * 2 * pi
  tm <- rotationMatrix(current.angle, 1,0,0)
  x.pos <- round(polyhedron.scale * sin(current.angle), 2)
  y.pos <- round(polyhedron.scale * cos(current.angle), 2)
  tm <- tm %*% translationMatrix(x.pos,y.pos,0)
  print(paste("Drawing ",polyhedron.name," rotated ", round(current.angle,2),
              " in (1,0,0) axis. Translated to (",x.pos,",",y.pos,",0)",
              " with color ",polyhedron.colors[i], sep = ""))
  shape.rgl <- polyhedron$getRGLModel(transformation.matrix = tm)
  shade3d(shape.rgl, color = polyhedron.colors[i])
}
```

